The symmetric \textit{Fermi} and eROSITA bubbles problem: A proof-of-concept study

### 2022-01-28 paper.tex
update

@@

\subsubsection{Leptonic process}
In the leptonic scenario, the gamma-rays originate from IC scattering of the ISRF by CRe.\
The CRe spectrum follows a power law distribution\
with a spectral index $p=2.4$ and ranges from\
$m_{\text{e}}c^2$ ($0.5$ MeV) to $1.1\times10^{6}m_{\text{e}}c^2$ ($0.55$ TeV).\

@@

\begin{figure}
  \includegraphics[width=\linewidth]{figures/fig__spectrum.png}
  \caption{
      Simulated gamma-ray spectra (top) of the Fermi bubbles calculated for a longitude range of\
      $|l|<10^{\circ}$ for different latitude bins.\
      The gray band represents the observational data of \citet{Ackermann2014}.\
      Microwave spectra (bottom) averaged over $|l|<10^{\circ}$, $20^{\circ}<|b|<30^{\circ}$.\
      The data point represents the \textit{WMAP} data in the 23 GHz K band and the shaded area indicates the range\
      of synchrotron spectral indices allowed for the \textit{WMAP} haze \citep{Dobler_2008}.
  }
  \label{fig__gammaRay}
\end{figure}

>>>>

  To quantify the synchrotron radiation as a function of position, it\
  is essential to start the simulation with a more realistic magnetic\
  field distribution. To this end, for our fixed magnetic field we adopt\
  the default exponential model in \textsc{galprop} \citep{Strong2007}
  which has the following spatial dependence:\

  \begin{equation}
     |\mathbf{B}(R, z)|=B_{0}\exp{-z/z_{0}}\exp{-R/R_{0}},
  \end{equation}

  where $R=\sqrt{x^{2}+y^{2}}$, $B_{0}$ is the average field strength at the GC\
  and $z_{0}$ and $R_{0}$ are the characteristic scales in the vertical and radial\
  directions, respectively. We adopt $z_{0} = 2$ kpc and $R_{0} = 10$ kpc, which\
  are best-fitting values in the \textsc{galprop} model to reproduce the\
  observed large-scale 408 MHz synchrotron radiation in the Galaxy.\
  We choose $B_{0} = 50$ $\mu$G based on the observed field strength at the\
  GC \citep{Crocker2010}.

@@

\subsubsection{Leptonic process}
In the leptonic scenario, the gamma-rays originate from IC scattering of the ISRF by CRe.\
The CRe spectrum follows a power law distribution\
with a spectral index $p=2.4$ and ranges from\
$m_{\text{e}}c^2$ ($0.5$ MeV) to $1.1\times10^{6}m_{\text{e}}c^2$ ($550$ GeV).\

@@

\begin{figure}
  \includegraphics[width=\linewidth]{figures/fig__spectrum.png}
  \caption{
      Simulated gamma-ray spectra (colored lines in top panel) of the Fermi bubbles calculated for a longitude range of\
      $|l|<10^{\circ}$ for different latitude bins.\
      The gray band represents the observational data of \citet{Ackermann2014}.\
      Simulated microwave spectra (colored lines in bottom) averaged over $|l|<10^{\circ}$, $20^{\circ}<|b|<30^{\circ}$.\
      The data point represents the \textit{WMAP} data in the 23 GHz K band and the shaded area indicates the range\
      of synchrotron spectral indices allowed for the \textit{WMAP} haze \citep{Dobler_2008}.
  }
  \label{fig__gammaRay}
\end{figure}
